---
title: "Assessment2"
author: "Pakkapong s4658734"
date: '2022-03-17'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## *Pakkapong Karnjanapatchara* **s4658734**

-----------------------------------------------------------------

# Assignment 2

##Load Dataset

```{r}

library(tidyverse)

thanksgiving_meal <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-11-20/thanksgiving_meals.csv")

```

**1. Display the first 10 rows of the dataset using `kable()` function (1 marks).**

```{r}

library(knitr)

kable(thanksgiving_meal[1:10, ])
      
```


**2. Using `skim()` display the summary of variables.**

```{r}

library(skimr)

skim(thanksgiving_meal)

```

**Think about the task to predict a family income based on their menu: what variables may be useful? Are all of them correct type?  Write 2-3 sentences with your explanation. (2 marks)**

To predict a family income based on their menu, the useful variables could be 'main_dish' which contains 8 different values and 'cranberry' which contains 4 types of value. The variety of different values could increase the accuracy of prediction.

**Think about the task to predict a community type or US_region based on their menu: what variables may be useful? Are all of them correct type? (2 marks)**

To predict a community type based on their menu, the useful variables could be 'cranberry' which contains 4 different values(Canned, Homemade, None, Other) and 'side1-15' which contains only 2 values in each variable. The different values of cranberry and the vegetables of side1-15 might have a significant to indicate the community type.

**3. Use `fct_reorder` and `parse_number` functions to create a factor variable `family_income`(2 mark).**

```{r}

thanksgiving_meal <- thanksgiving_meal %>%
  mutate(family_income = fct_reorder(family_income, parse_number(family_income)))

class(thanksgiving_meal$family_income)


```

**4. What is the number of people who celebrate? (1 mark)**

There are 980 people who celebrate.

```{r}

thanksgiving_meal %>%
  count(celebrate) %>%
  kable()

```


**5. What are categories and insights for each main dish served and the method it is prepared? (2 marks)**

```{r}

thanksgiving_meal %>%
  summarise(main_dish, main_prep) %>%
  count(main_dish, main_prep) %>%
  kable()

```

For Chicken, the most popular methods are Baked(4) and Roasted(4). 

For Ham/pork, the most popular method is Baked(22), following by Roasted(5).

For Roastbeef, the most popuplar method is obviously Roasted(5).

For Tofurkey, the most popular method is Baked(14) followed by Roasted(4).

For Turkey, the most popular method is Baked(422) followed by Roasted(351).

There is only one method for Turducken which is Roasted(3).

**6. Create 3 different data viz showing insights for main dish served and the method. Provide your own legend and use themes. Write 2-3 sentences with your explanation of each insight. (4 marks)**

```{r}

thanksgiving_meal %>%
  count(main_prep, main_dish) %>%
  ggplot(aes(main_dish, n)) +
  geom_col() +
  facet_wrap(~main_prep) +
  coord_flip() +
  theme_bw() +
  labs(title = "VIZ1 - Number of MAINDISH by Preparation Methods", x = "Menu", y = "n")
```

According to VIZ1, The most popular main dish is Turkey. The top 3 of preparation methods for Turkey include 1. Baked 2. Roasted 3. Fried

```{r}
thanksgiving_meal %>%
  count(main_dish, main_prep, age) %>%
  ggplot(aes(main_dish, n, fill = main_prep)) +
  geom_col() +
  facet_wrap(~age) +
  coord_flip() +
  theme_gray() +
  labs(title = "VIZ2 - Distribution of Maindish & Method in the different ranges of age", fill = "Method", x = "MainDish", y = "n")
```

According to VIZ2, People in age between 45-59 consume the highest number of Ham/Pork. While, people in age of 60+ have the lowest number of Ham/Pork consumption. 

```{r}
thanksgiving_meal %>%
  count(main_dish, main_prep, community_type) %>%
  ggplot(aes(main_dish, n, fill = main_prep)) +
  geom_col() +
  coord_flip() +
  facet_wrap(~community_type) +
  labs(x = "MAINDISH", y = "n", fill = "Method", title = "VIZ3 - MainDish & MainPrep classified by Community type")


```

According to VIZ3, there is no significantly different consumption of Turkey and its cooking method among the different community types.

The highest roasted beef consumption is in Urban area. The highest Baked Ham/Pork is in Sub-Urban area.

**7. How many use cranberry sauce? How many use gravy? 2marks**

There are 828 observations use cranberry sauce.

There are 892 observations use gravy.

```{r}

thanksgiving_meal %>%
  count(cranberry) %>%
  kable()



thanksgiving_meal %>%
  count(gravy) %>%
  kable()
```


**8-9. What is the distribution of those who celebrate across income ranges. Create a data viz. Write 2-3 sentences with your explanation of each insight. (4 marks)**

```{r}

thanksgiving_meal %>%
  count(family_income, celebrate) %>%
  ggplot(aes(family_income, n, fill = celebrate)) +
  geom_col() +
  facet_grid(~celebrate) +
  coord_flip()


```

The highest number of people who celebrate have income range between '$25,000 to $49,999'. While, the lowest income range of people who celebrate is between '$17,000 to 199,999$'.

The two highest number of people who do not celebrate have income range between '$0 to $9,999' and '$25,000 to $49,999'. While, the two lowest income ranges of people who do not celebrate are between '$125,000 to 149,999$' and '$175,000 to $199,999'.



**10. Use the following code to create a new data set 2 mark. Write 2-3 sentences with your explanation of what it does. (4 marks)**

```{r}
thanksgiving_meal_new <- thanksgiving_meal %>%
  select(id, starts_with("side"),
       starts_with("pie"),
       starts_with("dessert")) %>%
  select(-side15, -pie13, -dessert12) %>%
  gather(type, value, -id) %>%
  filter(!is.na(value),
         !value %in% c("None", "Other (please specify)")) %>%
  mutate(type = str_remove(type, "\\d+"))
```

The code creates a new dataset that combine all variables of side(1-15), pie(1-13), and dessert(1-12) into one column. The code gathers type, id and also filter only usable value.

**11-12. Intall package `widyr` and use `pairwise_cor()` function. Write 2-3 sentences with your explanation of what it does. (2 marks)** 

The code does compute the Correlations of pairs of items. In this new dataset, the code shows the correlation of values of side, pie, dessert in descending order.

**Write 1 sentence with your explanation of what insights it shows. (2 marks)**

The pair that has the highest correlation (0.411) is Cookies and Brownies. The lowest correlation (-0.164) is the pair of Pumpkin and Macaroni and cheese.

```{r}

#install.packages('widyr')

library(widyr)

thanksgiving_meal_new %>%
  pairwise_cor(value, id, sort = TRUE)


```


**13. Use `lm()` or randomForest() function to build a model that predict a family income based on data in the dataset. 8 marks**

**Compare 3 models using different set of input variables. Use different number of variables. Explain your choice of variables (3 sentences).**

To predict family income, There are 3 variables chosen as an input for the first model including main_dish, cranberry, and gender

To predict family income, There are 4 variables chosen as an input for the second model including cranberry, community_type, gender, and age

To predict family income, There are 7 variables chosen as an input for the third model including main_dish, main_prep, cranberry, age, gender, kid_table_age, and prayer 

**Write 2 sentences explaining which model is best.**

According to the results, it appears that the second model is the best out of 3 different models because it has the lowest error rate. The more variable doesn't always provide the better result.

Assumption from model 2:

Male might have more income than female.

Homemade cranberry consumer might have less income than canned cranberry consumer.

Old age might have more income than young age.

Urban might have more income than Rural


```{r}
#install.packages("randomForest")

library(randomForest)

rf1 <- randomForest(family_income ~ main_dish + cranberry + gender, data = thanksgiving_meal, na.action = na.omit)

print(rf1)

rf2 <- randomForest(family_income ~ cranberry + community_type + gender + age, data = thanksgiving_meal, na.action = na.omit)

print(rf2)

rf3 <- randomForest(family_income ~ main_dish + main_prep + cranberry + age  + gender + kids_table_age + prayer, data = thanksgiving_meal, na.action = na.omit)

print(rf3)
```

